---
title: "Codeswitching VOT - Pilot Data"
author: "Marguerite CAMERON"
date: "22 décembre 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intro 

These are dataframes containing the name of the participant and a small sample of the VOT measurements taken from the pilot experiment. 
VOT measurements were taken from recordings of spontaneous speech, and are of word-initial [p], [t], or [k].  There are 10 VOT samples in each category (explained below).  The words selected to comprise the data for this project are the first 10 with easy and reliable VOT measurements in the folder of audio clips from the original recording.  The 10 VOT measurements in each category are, then, quasi-random.

VOT measurements (in ms) for each participant are taken first from French words in a monolingual French context and second from English codeswitch words in a predominantly French conversational context.

The first participant, F, is a native francophone bilingual in English.  Her data frame will contain two categories of VOT measurements.  The first, which will be named "L1", is of French words in a monolingual context.  The second, which will be named "L1toL2", is of English words during a predominantly French conversation.  

The second participant, P, is a native anglophone bilingual in French.  Her data frame will also contain two categories of VOT measurements.  The first, which will be named "L2", is of French words in a monolingual context.  The second, which will be named "L2toL1", is of English words during a predominantly French conversation.

The analyses that follow are intended to provide a comparison of two speakers of different native languages in their average French VOTs and their average English VOTs in instances of French to English codeswitching.
Using this sample data, predictions will be made for what to expect of more data from the same speakers or of a larger, hypothetical data set.


## Data frames for each participant

Data frames include :
The name of the participant, the phoneme whose VOT was measured, and the VOT of the corresponding phoneme.

```{r}
# Participant F

participant_F <- c('F')
L1phone <- c('k', 'k', 'k', 'p', 'p', 'p', 'p', 't', 'p', 'p')
L1 <- c(24, 14, 25, 14, 22, 14, 13, 37, 13, 21)
L1toL2phone <- c('k','k','k','k','k', 'p', 'p', 'k','k', 't')
L1toL2 <- c(50, 30, 29, 44, 48, 45, 65, 30, 42, 54)

F.data <- data.frame(participant_F, L1phone, L1, L1toL2phone, L1toL2 )

summary(F.data)

print(F.data)
```


```{r}
# Participant P

participant_P <- c('P')
L2phone <- c('p', 'p', 'p', 'p', 'p', 'p', 'p', 'p', 'p', 't')
L2 <- c(9, 13, 18, 11, 11, 16, 10, 27, 10, 19)
L2toL1phone <- c('p', 't', 't', 'p', 'p', 'p', 'k', 't', 'p', 'p')
L2toL1 <- c(49, 65, 67, 23, 17, 31, 51, 49, 59, 36)

P.data <- data.frame(participant_P, L2phone, L2, L2toL1phone, L2toL1)

summary(P.data)

print(P.data)
```


## Boxplots and Histograms for Original Data of Each Participant

The boxplots provide a basic visual comparison of the original data for each participant.  Though looking at the tables, there are clearly differences between their respective VOTs in the two conditions, a visual representation is useful for quickly comparing the two.

```{r}
# Boxplot for Participant F
# shows basic comparison between VOT for French monolingual context and for English words during a codeswitch

boxplot(L1, L1toL2)

# Histogram for L1 VOTs for Participant F

hist(F.data$L1, main="French VOTs of Particpant F", xlab = "VOT (ms)")

# Histogram for L1toL2 VOTs for Participant F

hist(F.data$L1toL2, main="English Codeswitch VOTs of Particpant F", xlab = "VOT (ms)")

```

```{r}

# Boxplot for Participant P
# shows basic comparison between VOT for French monolingual context and for English words during a codeswitch

boxplot(L2, L2toL1)

# Histogram for L2 VOTs for Participant P

hist(P.data$L2, main="French VOTs of Particpant F", xlab = "VOT (ms)")

# Histogram for L2toL1 VOTs for Participant P

hist(P.data$L2toL1, main="English Codeswitch VOTs of Particpant P", xlab = "VOT (ms)")
```




## Initial comparison of the two speakers, based on the original sample data 

Based on the original sample data, we can make some rudimentary observations about the two speakers' articulatory patterns.

Unexpectedly, Participant P has displayed a shorter VOT in a French monolingual context, on average.  This is surprising for two reasons : as an anglophone, Participant P would be predicted to have longer VOT than a francophone native, and -- though this has not been factored in to the present analysis -- Participant P has a generally slower speech rate than that of Participant F.
That said, the difference in mean VOT in French monolingual contexts is quite small within the original sample size -- a mean of 19.7 for Participant F and of 14.4 for Participant P.  

There is a smaller difference between the two speakers' mean VOTs in the French to English codeswitching environment.  

From the boxplots, it can be noted that, for both speakers, there is greater variety in the measured VOTs in the codeswitching condition, especially with Participant P.  Whereas in the French monolingual condition, both speakers' VOTs are more tightly grouped around the mean.  


## Expansion of the dataset by resampling

Using a basic bootstrap function, more datapoints will be generated to allow for comparison between the two speakers.


```{r}

library(boot)

participant_F <- c('F')
L1phone <- c('k', 'k', 'k', 'p', 'p', 'p', 'p', 't', 'p', 'p')
L1 <- c(24, 14, 25, 14, 22, 14, 13, 37, 13, 21)
L1toL2phone <- c('k','k','k','k','k', 'p', 'p', 'k','k', 't')
L1toL2 <- c(50, 30, 29, 44, 48, 45, 65, 30, 42, 54)

F.data <- data.frame(participant_F, L1phone, L1, L1toL2phone, L1toL2 )

Participant_F_boot <- boot(data=F.data, statistic=L1, R=100)
```


